sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2018-05-18 inst/documents/sensi_an_rotations1.Rmd
paper3 writing
paper3

# Starting question : is there any benefit to rotations when there are no costs and no migration to an untreated area ?
# 
# Test 1. No refugia (i.e. Coverage=100%) or fitness costs. Would expect all policies to be equivalent.
# 
# Test 2. Dominance of resistance and fitness costs both set to 0.5.
# I suspect one of the advantages of rotations (and the presence of refugia) is that they maintain lower resistance allele frequencies which slows the spread of recessive resistance alleles. I suspect/guess/intuit that if we make them semi-dominate these effects should disappear and all policies should be the same. I’m probably wrong but it’s a nice test…..
# 
# 
# Testing sensitvity analysis to answer question 1. Are sequences and rotations equivalent when coverage 100% and no fitness costs. On each page should see a run with 1 set of inputs first for sequence then for rotation.

@@

# set random seed so that results can be reproduced
#set.seed(1)
set.seed(2)
max_gen         <- 500
plot_scenarios  <- FALSE
n_scenarios     <- 10000 # try 1000 runs with no cost
already_ran     <- FALSE
#already_ran     <- TRUE

@@

    ## constant inputs ##
    #linputs$coverage <- 1
    #linputs$migration <- 0
    #linputs$cost <- 0 #variable cost below
    linputs$max_gen <- max_gen

    #beware min_rwr_interval, it's to stop repeated small rotations
    linputs$min_rwr_interval = 5
    #set plot to F if using grid.arrange as in phaps-rotations-better.Rmd
    linputs$plot <-     FALSE

    ## variable inputs ##
    linputs$cost <-           runif(1, min=0,   max=0.1) 
    #linputs$cost <-           0 
    linputs$expo_hi <-        runif(1, min=0.4, max=0.9)  #min=0.1, max=0.9
    linputs$male_expo_prop <- runif(1, min=0,   max=1)
    linputs$eff <-            runif(1, min=0.5, max=1) # min=0.3, max=1
    linputs$rr  <-            runif(1, min=0.1, max=0.9)
    linputs$dom_sel <-        runif(1, min=0,   max=1)
    linputs$dom_cos <-        runif(1, min=0,   max=1) 
    linputs$start_freqs <-    runif(1, min=0.005,   max=0.1) #note not log yet   
    linputs$n_insecticides <- sample( 2:5, 1 )  #beware set replace=T if more than 1
    # dispersal (initially with cost set to 0)
    linputs$coverage <-       runif(1, min=0.1, max=0.9)
    linputs$migration <-      runif(1, min=0.1, max=0.9)

>>>>

# Starting question : is there any benefit to rotations when there are no costs and no migration to an untreated area ?
# 
# Test 1. No refugia (i.e. Coverage=100%) or fitness costs. Would expect all policies to be equivalent.
# 
# Test 2. Dominance of resistance and fitness costs both set to 0.5.
# I suspect one of the advantages of rotations (and the presence of refugia) is that they maintain lower resistance allele frequencies which slows the spread of recessive resistance alleles. I suspect/guess/intuit that if we make them semi-dominate these effects should disappear and all policies should be the same. I’m probably wrong but it’s a nice test…..
#

@@

# set random seed so that results can be reproduced
#set.seed(1)
set.seed(2)
max_gen         <- 500
plot_scenarios  <- FALSE
n_scenarios     <- 10000 
already_ran     <- FALSE
#already_ran     <- TRUE

@@

    ## constant inputs ##
    linputs$coverage <- 1
    linputs$migration <- 0
    linputs$cost <- 0 #variable cost below
    linputs$max_gen <- max_gen

    #beware min_rwr_interval, it's to stop repeated small rotations
    linputs$min_rwr_interval = 1
    linputs$min_gens_switch_back <- 5
    #set plot to F if using grid.arrange as in phaps-rotations-better.Rmd
    linputs$plot <-     FALSE

    ## variable inputs ##
    #linputs$cost <-           runif(1, min=0,   max=0.1) 
    #linputs$cost <-           0 
    linputs$expo_hi <-        runif(1, min=0.4, max=0.9)  #min=0.1, max=0.9
    linputs$male_expo_prop <- runif(1, min=0,   max=1)
    linputs$eff <-            runif(1, min=0.5, max=1) # min=0.3, max=1
    linputs$rr  <-            runif(1, min=0.1, max=0.9)
    linputs$dom_sel <-        runif(1, min=0,   max=1)
    linputs$dom_cos <-        runif(1, min=0,   max=1) 
    linputs$start_freqs <-    runif(1, min=0.005,   max=0.1) #note not log yet   
    linputs$n_insecticides <- sample( 2:5, 1 )  #beware set replace=T if more than 1
    # dispersal (initially with cost set to 0)
    #linputs$coverage <-       runif(1, min=0.1, max=0.9)
    #linputs$migration <-      runif(1, min=0.1, max=0.9)
